Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
bios and ack

\section{The WebBox EHR Platform}

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To address this deficiency, we have devised a personal data platform ``WebBox \cite{webbox}'', optimised to handle the secure, long-term storage of structured data at large volume.  Thus far, WebBox has been used to archive clinician (hospital and GP-provided) data, including both raw structured data (such as clinical diagnostic results) and accompanying report documents.  Being optimised for structured data capture and integration, our current work extends this platform to the aforementioned activity profiles, created from retrieving raw sensed data from digital health device APIs and translating such observations to the Activity-SENSE representation.

%Following this, to optionally share these annotations, along with their activity diaries, with their clinician. This then enables clinicians and patients to enter into a dialog about how well the patient is doing, and any lifestyle changes they can make to better their situation.

%% Furthermore, Therefore, existing platforms for storing EHRs may
%% prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
%% would enable clinicians and patients to view the data in context.

@@

%\section{Biographies}

>>>>

The data collected by patients' devices has the potential to create a large volumes of highly structured data. Some sensors
are collecting minute-by-minute data values form multiple sensors 24 hours a day, whereas 
EHRs tend to contain individual records for each clinical session. Therefore, existing methods of storing EHRs may
prove to be unsuitable for the large volumes of data from activity diaries. However, integrating with existing EHRs
would enable clinicians and patients to view the data in context.

To this challenge we present our own personal data platform ``WebBox \cite{webbox}.'' We have used WebBox with EHRs
to enable patient collected data to be augmented with hospital-provided EHR data. WebBox is able to combine
data from multiple sources, and enables patients to make their own annotations against data, and
to optionally share these annotations, along with their activity diaries, with their clinician. This
then enables clinicians and patients to enter into a dialog about how well the patient is doing,
and any lifestyle changes they can make to better their situation.

@@

\section{Biographies}

\subsection{Daniel A. Smith and Max Van Kleek}

Daniel and Max are postdoctoral researchers on the SOCIAM project at the University of Southampton, and the principal architects of the WebBox
personal information store. They have research interests in HCI, the Semantic Web and Personal Information Management.

\subsection{Nigel R. Shadbolt}

Nigel Shadbolt (FBCS FREng) is Professor of Artificial Intelligence and Head of the Web and Internet Science Group, University of Southampton. He is the Chairman and Co-Founder of the Open Data Institute, Director of the Web Science Trust, and of the Web Foundation.  He and Sir Tim Berners-Lee were appointmented as Information Advisors to the UK Government, leading to \url{data.gov.uk}. He is a member of the Public Sector Transparency Board, and Chair of the UK Government’s midata programme.

\section{Key Technology: WebBox}

WebBox is...

\section{Acknowledgement}

This work is supported under SOCIAM: The Theory and Practice of Social Machines.  The SOCIAM Project is funded by the UK Engineering and Physical Research Council (ESPRC) under grant number EP/J017728/1 and comprises the Universities of Southampton, Oxford and Edinburgh.
